Reordering snacks is effective and just

### 2016-03-10 trunk/snacks/paper.tex
First submitted version

\usepackage{amsthm}
\usepackage{relsize}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{code}
\usepackage{graphicx}
\usepackage{fancyvrb}
\usepackage{url}
\usepackage{textcomp}

@@

\title{Snacking policies}
\author{Dr.~Tom~Murphy~VII~Ph.D.\thanks{
    Copyright \copyright\ 2016 the Regents of the Wikiplia Foundation.
    Appears in SIGBOVIK 2016 with the haunting memory of the
    Association for Computational Heresy; {\em IEEEEEE!} press,
    Verlag--Verlag volume no.~0x2016. ANG 0.00} }

@@

\begin{abstract}
% XXX better abstract
what do I put here
\end{abstract}

\vspace{1em}
{\noindent \small {\bf Keywords}:
  snacking, consequentialism, comestability theory
}

@@

One strategy is for this worker, who we will call Sal, to take all of the favored Cherry-Vanilla foods from the kitchenette to his desk at the beginning of the day. This strategy is called hoarding. This ensures that Sal may eat all his Cherry-Vanilla flavors. However, this behavior is considered unfair, for one reason that all other workers are completely deprived of Cherry-Vanilla flavor. It is perceived that Sal and all other workers should have equivalent access to the shared resource, except for the moment that he is selecting a food (for he is ``first in line,'' and lines are fair). Moreover, Sal should take only one food at a time (for it is ``Please help yourself. We ask that you take only one piece so that others may enjoy it as well,'' which is fair). We also perceive that Sal should take food only when he is actually hungry (for it is ``waste not, want not,'' and you can't spell ``aphorism'' without ``a fair is,'' mmm?).

@@

Note that the author does not reorder habitually reorder snacks; this question is of abstract philosophical interest. We consulted the wisdom of Judge John~Hodgman, who wrote~\cite{hodgman2016snacks}:

@@

@@

A simulation consists of an array $S$ of shelves, each of which is stocked with different varieties of food. The varieties are just given as integers from 0--$n_i$, where each food type (shelf) may have a different number of varieties. In an early version of the simulation each food and variety is given a name, so we might have a shelf consisting of many sodas, like\footnote{All of these brands now Copyright Trademark Patent Pending Dr.~Tom Murphy VII Ph.D., 2016!}

@@

\begin{enumerate}
\item Selects a shelf at random.
\item Sets her gaze upon the foremost variety on that shelf. She has some value $v$ for this item, given by $P$. \label{step:start}
\item She can see the number of items on the shelf, but not what varieties they are. From this number, she estimates what value $v'$ she would get from skipping the current variety (for this round) and setting her gaze upon the next one. \label{step:skip}
\item If $v' > v$, she does so, and repeats from step \ref{step:skip}.
\item If not, this is the food provisionally selected for this shelf, with value $v$.
\item If there are shelves remaining, she estimates the value of abandoning this shelf and trying the next one, $v''$.
\item If $v'' > v$, she moves to the next shelf and returns to step \ref{step:start}.
\item If she finishes with a selected food, she may reorder the items on the shelf of that food arbitrarily. She removes the selected food, if any, and eats it.
\end{enumerate}

@@

This does not match our intuitions of how real workers behave. Most of the time, an indifferent worker will just take a food that is ``good enough;'' this is known as ``satisficing.''\cite{simon1956rational} To prevent this, a worker's estimate of the value of continuing to search the shelf will include a small cost to search each item. This can be thought of as the cost of the physical labor or the displaced opportunity cost, or an estimate of the risk that an interruption causes her to have to stop searching before she selects a snack.

@@

I then generated random scenarios and evaluated different snack
reordering policies. One extreme policy sorts the shelf in reverse
preference order, so that the worker's favorite snacks are at the
back. This seems unnecessary (takes $\mathrm{O}(n \mathrm{lg} n)$
time, unless perhaps using ``radix sort'') and unrealistic. It also
leads to substantial interference between workers, as one worker's
resorting completely undoes another's. Another relaxation of this,
more realistic, is where the worker only moves his favorite variety to
the depths of the shelf. This is analogous to a ``Move-to-Back
List''~\cite{rivest1976self}, except not really, since the worker
somehow finds all of the instances of their favorite variety in the
whole shelf before moving them to the back. The most realistic policy
generalizes this last one, and only moves the favorite snack when it
passes some ``outlier'' threshold for how much it is preferred over
the other snacks. This is the policy I ran many experiments for.

@@

Normally, this is where a heroic scientist would (a) implicate the
model, seeing as how it fails to have intuitive properties\footnote{I
  think that the model does not capture two important aspects. First
  is that Sal \emph{does know} that he's reordered the snacks and can
  likely find his favorites by just looking immediately to the back.
  Second is that traces of the model suggest that most workers look
  through nearly all of the snacks due to the (rational) expectation
  that they will improve their selection. There does not seem to be a
  good setting of the {\tt COST\_TO\_LOOK} penalty that suitably
  discourages workers from looking through the whole shelf while still
  allowing a resorter to find his deeply-placed favorites.} or (b)
give up. But owing to Draconian SIGBOVIK deadlines, this heroic
scientist resorts to another unjustifiable but common technique:
``Tweaking'' the model parameters until the experiments turn out as
expected (i.e., positive). Better yet, this process can be automated!

\medskip
Overnight in 4 separate browser tabs I ran a simple ``hyper-parameter
search'' to try to find the best settings of the parameters described
previously. I selected parameter values uniformly at random, and then
interpolated against the current local maximum (by averaging the
random point with the best point for each successive ``heads''
coin-flip during intialization). The goal was to find parameters that
simultaneously improved two scores in the experiment: The value of the
snacks eaten by the resorting worker, and the total value of snacks
eaten across all workers. (Specifically, I maximized the minimum of
these two). The best settings of the model had these values:

\begin{tabular}{@{\hspace{0.5in}}lr}
\verb+COST_TO_LOOK+ & 0.001 \\
\verb+MAX_ITEMS+ & 37 \\
\verb+MAX_VARIETY+ & 4 \\
\verb+MEAN_WAIT+ & 36305.715 \\
\verb+MIN_ITEMS+ & 3 \\
\verb+MRATIO+ & 1.010 \\
\verb+NUM_PEOPLE+ & 2 \\
\verb+NUM_SHELVES+ & 15 \\
\verb+OUTLIER_RATIO+ & 2.199 \\
\verb+PREF_MEAN+ & 1.320 \\
\verb+PREF_STDDEV+ & 5.625 \\
\end{tabular}

>>>>

\usepackage{supertabular}
\usepackage{amsthm}
\usepackage{relsize}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{code}
\usepackage{graphicx}
\usepackage{fancyvrb}
\usepackage{url}
\usepackage{textcomp}

@@

\title{Reordering snacks is effective and just}
\author{Dr.~Tom~Murphy~VII~Ph.D.\thanks{
    Copyright \copyright\ 2016 the Regents of the Wikiplia Foundation.
    Appears in SIGBOVIK 2016 with the haunting memory of the
    Association for Computational Heresy; {\em IEEEEEE!} press,
    Verlag--Verlag volume no.~0x2016. ANG 0.00} }

@@

\section*{Concrete}
It's time to get serious about {\em snacks} and {\em stats}.

\vspace{1em}
{\noindent \small {\bf Keywords}:
  snacking, permutations, comestability theory
}

@@

One strategy is for this worker, who we will call Sal, to take all of the favored Cherry-Vanilla foods from the kitchenette to his desk at the beginning of the day. This strategy is called Hoarding. This ensures that Sal may eat all his Cherry-Vanilla flavors. However, this behavior is considered unfair, for one reason that all other workers are completely deprived of Cherry-Vanilla flavor. It is perceived that Sal and all other workers should have equivalent access to the shared resource, except for the moment that he is selecting a food (for he is ``first in line,'' and lines are fair). Moreover, Sal should take only one food at a time (for it is ``Please help yourself. We ask that you take only one piece so that others may enjoy it as well,'' which is fair). We also perceive that Sal should take food only when he is actually hungry (for it is ``waste not, want not,'' and you can't spell ``aphorism'' without ``a fair is,'' mmm?).

@@

Note that the author does not reorder habitually reorder snacks; this question is of abstract philosophical interest. We consulted the wisdom of Judge John~Hodgman, who ruled~\cite{hodgman2016snacks}:

@@

\subsection{Why Reorder?}

As suggested before, Reordering benefits Sal because his favorite snacks are less likely to be eaten by others. The policy can be thought of as fair because it still provides everyone equivalent access to the snacks. But did Sal make the snacks worse for everyone by putting the good snacks at the back? The problem seems intractible until we consider an unjustifiable but standard simplifying assumption: Each worker's preferences for snacks are independent and identically distributed. This means that Sal's preference for Cherry-Vanilla gives us no information about the rest of the workforce's preferences. Since all preferences are equally likely, reordering the snacks improves access to some snacks and hinders access to others; these effects cancel out. Thus under suitable assumptions, {\it any} reordering of snacks is fair and harmless to other workers. The reason why we believe that this particular policy is beneficial is that other workers may be indifferent among various flavors, and simply take the one that is most convenient. When indifferent, taking a variety that someone else substantially favors is globally sub-optimal. This is similar to the principle of ``decoy beer'', whereby cheap OK beer (e.g. Red Stripe) is placed at the front of the fridge in front of the premium good beer (which may be unsuitable for casual drinkers anyway).

We can go further and demonstrate this scientifically.

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=\linewidth]{shelves}
\end{center}\vspace{-0.1in}
\caption{Two shelves with snacks. Shelf~1 has four snacks; potentially different types of Y\"o!gurt brand yogurt. Shelf~2 has six snacks, potentially different types CHIPz brand natural particle chips. I can tell you that the first three on Shelf~1 are Cherry flavor, and the last one is the Diet Cherry variety. All of the CHIPz are different varieties: Dust flavor, Dirt flavor, Sticks flavor, Cobweb flavor, Sand flavor, and Powder flavor. But because of the way snacks are arranged, you can only see the variety of the snack in front.} \label{figure:shelves}
\end{figure}

A simulation consists of an array $S$ of shelves, each of which is stocked with different varieties of food (Figure~\ref{figure:shelves}). The varieties are just given as integers from 0--$V_i$, where each food type (shelf) may have a different number of varieties. In an early version of the simulation each food and variety is given a name, so we might have a shelf consisting of many sodas, like\footnote{All of these brands now Copyright Trademark Patent Pending Dr.~Tom Murphy VII Ph.D., 2016!}

@@

\begin{enumerate}
\item Selects a shelf at random.
\item Sets her gaze upon the foremost variety on that shelf. She has some value $v$ for this item, given by $P$. \label{step:start}
\item She can see the number of items on the shelf, but not what varieties they are. From this number, she estimates what value $v'$ she would get from skipping the current variety (for this round) and setting her gaze upon the next one. \label{step:skip}
\item If $v' > v$, she does so, and repeats from step \ref{step:skip}.
\item If not, this is the food provisionally selected for this shelf, with value $v$.
\item If there are unvisited shelves remaining, she estimates the value of abandoning this shelf and trying the next one, $v''$.
\item If $v'' > v$, she moves to the next shelf and returns to step \ref{step:start}.
\item If she finishes with a selected food, she may reorder the items on the shelf of that food arbitrarily. She removes the selected food, if any, and eats it.
\end{enumerate}

@@

This does not match our intuitions of how real workers behave. Most of the time, an indifferent worker will just take a food that is ``good enough;'' this is known as ``satisficing.''\cite{simon1956rational} The argument for the global value of Sal reordering hinges on such indifference, in fact. To prevent this, a worker's estimate of the value of continuing to search the shelf will include a small cost to search each item. This can be thought of as the cost of the physical labor or the displaced opportunity cost, or an estimate of the risk that an interruption causes her to have to stop searching before she selects a snack.

@@

I then generated random scenarios and evaluated different snack
reordering policies. One extreme policy sorts the shelf in reverse
preference order, so that the worker's favorite snacks are at the
back. This seems unnecessary (takes $\mathrm{O}(n\ \mathrm{lg}\ n)$
time, unless perhaps using ``radix sort'') and unrealistic. It also
leads to substantial interference between workers, as one worker's
resorting completely undoes another's. Another relaxation of this,
more realistic, is where the worker only moves his favorite variety to
the depths of the shelf. This is analogous to a ``Move-to-Back
List''~\cite{rivest1976self}, except not really, since the worker
somehow finds all of the instances of their favorite variety in the
whole shelf before moving them to the back. The most realistic policy
generalizes this last one, and only moves the favorite snack when it
passes some ``outlier'' threshold for how much it is preferred over
the other snacks. This is the policy I ran many experiments for.

@@

Normally, this is where a heroic scientist would (a) implicate the
model, seeing as how it fails to have intuitive properties\footnote{I
  think that the model does not capture two important aspects. First
  is that Sal \emph{does know} that he's reordered the snacks and can
  likely find his favorites by just looking immediately to the back.
  Second is that traces of the model suggest that most workers look
  through nearly all of the snacks due to the (rational) expectation
  that they will improve their selection. There does not seem to be a
  good setting of the {\tt COST\_TO\_LOOK} penalty that suitably
  discourages workers from looking through the whole shelf while still
  allowing a resorter to find his deeply-placed favorites.} or (b)
appeal that ``it seems more work is needed in this fertile area of
study'' or (c) give up. But owing to Draconian SIGBOVIK deadlines,
this heroic scientist resorts to another unjustifiable but common
technique: ``Tweaking'' the model parameters until the experiments
turn out as expected (i.e., positive). Better yet, this process can be
automated!

\medskip
{\bf Search}.\ \ \ Overnight in 4 separate browser tabs I ran a simple ``hyper-parameter
search'' to try to find the best settings of the parameters described
previously. I selected parameter values uniformly at random, and then
interpolated against the current local maximum (by averaging the
random point with the best point for each successive ``heads''
coin-flip during intialization). The goal was to find parameters that
simultaneously improved two scores in the experiment: The value of the
snacks eaten by the resorting worker, and the total value of snacks
eaten across all workers. (Specifically, I maximized the minimum of
these two). The best settings of the model had these values:

\begin{supertabular}{@{\hspace{0.5in}}lr}
\verb+COST_TO_LOOK+ & 0.001 \\
\verb+MAX_ITEMS+ & 37 \\
\verb+MAX_VARIETY+ & 4 \\
\verb+MEAN_WAIT+ & 36305.715 \\
\verb+MIN_ITEMS+ & 3 \\
\verb+MRATIO+ & 1.010 \\
\verb+NUM_PEOPLE+ & 2 \\
\verb+NUM_SHELVES+ & 15 \\
\verb+OUTLIER_RATIO+ & 2.199 \\
\verb+PREF_MEAN+ & 1.320 \\
\verb+PREF_STDDEV+ & 5.625 \\
\end{supertabular}
